\documentclass[12pt]{eccm-ecfd_abstract}

%\usepackage{graphicx}
%\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amssymb}

\title{INSTRUCTIONS TO PREPARE A ONE PAGE ABSTRACT FOR THE
ECCM 6 AND FOR THE ECFD 7}

\author{First A. Author$^{1}$, Second B. Author$^{2}$ and Third C. Author$^{3}$}

\address{$^{1}$ Affiliation, Postal Address, E-mail address and URL
\and
$^{2}$ Affiliation, Postal Address, E-mail address and URL
\and
$^{3}$ Affiliation, Postal Address, E-mail address and URL}

\begin{document}

\noindent {\bf Keywords}: {\it Instructions, Multiphysics Problems, Applications, Computing Methods}
\vskip0.5cm

Authors are invited to submit electronically a one page abstract through the Congress web site before December 15, 2017. Abstracts should outline the main features, results and conclusions as well as their general significance, and contain relevant references.

The Abstract can be submitted directly in its final form. Authors will have the possibility of replacing the file by an updated version after the acceptance notification.

The Abstract should be written following the format. The file must be converted to Portable Document Format (PDF) before submission through the Congress web site. Other formats are not accepted by the system.

The Abstract must be written in English following this format template. It must contain the full name and full address of author/s. In the case of joint authorships, the name of the author who will actually present the paper at the Conference should be indicated with an asterisk. Papers can only be accepted on the understanding that they will be presented at the Conference.

Preliminary acceptance of the contribution will be communicated to the corresponding author by January 22, 2018.

Final acceptance of papers for presentation is conditional to receiving the final Abstract in format for publication and the payment of the presenting author's conference registration fee before March 15, 2018. Submission of full papers is not mandatory. Only one presentation per delegate is allowed.

For any question, please contact the ECCM-ECFD 2018 Conference Secretariat.
E-mail: eccm-ecfd2018\_sec@cimne.upc.edu.


\begin{thebibliography}{99}
\bibitem{Zienkiewicz}  O.C. Zienkiewicz, O.C. and  R.L. Taylor,  \textit{The finite element method}. 6th Edition, Elsevier, 2005.
\bibitem{OnCe93} E. O\~{n}ate and M. Cervera, Derivation of thin plate bending elements with one degree of freedom per node.
\textit{Engng. Comput.}, Vol. \textbf{10}, pp. 543--561, 1993. 
\end{thebibliography}

\end{document}


